---
title: "Visualizations"
output: html_notebook
---

Slope of the curve depends on the value of r and const i.e(In our paper it depends on c/k). In the simple case since we assume a symmetric influence, we can safely conclude that if either the historic influence or the current influence of the journal is high then the journal is most likely going to see a further increased in influence in the bear future.
The following graphs demonstrate this.

r << c/k

```{r}
r = runif(1)
s = runif(1)
const = runif(1)
print(r)
print(s)
print(const)
#p <- (exp(r*x)+const)/exp(r*x)
curve((exp(r*x)*s*x+const)/exp(r*x), -10,10,add=TRUE)
```
r>c/k


```{r}
r = runif(1)
s = runif(1)
const = runif(1)
print(r)
print(s)
print(const)
#p <- (exp(r*x)+const)/exp(r*x)
curve((exp(r*x)*s*x+const)/exp(r*x), -10,10,add=TRUE)
```
r<c/k
```{r}

r = runif(1)
s = runif(1)
const = runif(1)
print(r)
print(s)
print(const)
#p <- (exp(r*x)+const)/exp(r*x)
curve((exp(r*x)*s*x+const)/exp(r*x), -10,10,add=TRUE)
```

r>>c/k
```{r}
r = runif(1)
s = runif(1)
const = runif(1)
print(r)
#r = 0.1715303
print(s)
#s = 0.5407635
#const = 0.5407635
print(const)
#p <- (exp(r*x)+const)/exp(r*x)
curve((exp(r*x)*s*x+const)/exp(r*x), -10,10,add=TRUE)
```


